\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Discussion: Synthesis and main contributions

To synthesize, we have introduced in this paper a spiking neural network model with hetero-synaptic delays which we have trained and evaluated on a challenging motion detection task. The model was defined as optimally detecting spatio-temporal event-based motifs. and we have shown that by training on a dataset of natural images with realistic eye movements, it learns kernels similar to those found in the early visual cortex, of humans for instance. We have then shown that the response of the model has similar responses as found in biology. We have further evaluated the computational cost for this model if it would be implemented on neuromorphic hardware, showing that including hetero-synaptic delays may prove
to be a frugal computational solution for future neuroomorphic hardware but also a key to understand why spikes is one universal currency in neural information processing.

Let us highlight some novelties of the contributions reported in this paper. First, the generic hetero-synaptic model is formalized from first
principles of optimally detecting spatio-temporal event-based signal, while []  use a heuristic based on correlation, which we have proved to be less efficient. \note{compared to HOTS~\citep{lagorce_hots_2017} the weights are explainable as they directly give the logit (inverse sigmoid of the probability) for contributing to detect each spatio-temporal spiking motif.} The model learns simultaneously the weights and delays, while the polychronization model (Izhikevich 2006) only learns weights using STDP while delays are drawn randomly and theit values frozen. Moreover, the model is evaluated on a realistic task, while models such as the tempotron are tested on simplified problems~\citep{gutig_tempotron_2006}. Foremost, the main contribution is to bring forward a model which is adapted to any spatio-temporal spiking motifs and able to be trained in a supervised manner by giving a dataset of supervison pairs. This allows a more flexible definition of the model using this properly labelled dataset instead of relying on a minute description of the physical rules governing a task, for instance the luminance conservation principle for motion detection~\citep{benosman_asynchronous_2012, dardelet}  (Benosman 2012, Dardelet 2021).

>>>>

To synthesize, we have introduced in this paper a spiking neural network model with hetero-synaptic delays which we have trained and evaluated on a challenging motion detection task. The model was defined as optimally detecting spatio-temporal event-based motifs. and we have shown that by training on a dataset of natural images with realistic eye movements, it learns kernels similar to those found in the early visual cortex, of humans for instance. We have then shown that the response of the model has similar responses as found in biology. We have further evaluated the computational cost for this model if it would be implemented on neuromorphic hardware, showing that including hetero-synaptic delays may prove to be a frugal computational solution for future neuromorphic hardware but also a key to understand why spikes is one universal currency in neural information processing.

Let us highlight some novelties of the contributions reported in this paper. First, the generic hetero-synaptic model is formalized from first principles of optimally detecting spatio-temporal event-based signal, while []  use a heuristic based on correlation, which we have proved to be less efficient. In addition, compared to HOTS~\citep{lagorce_hots_2017} the weights are explainable as they directly give the logit (inverse sigmoid of the probability) for contributing to detect each spatio-temporal spiking motif. Another novelty is that the model learns simultaneously the weights and delays, while for instance the polychronization model~\citep{Izhikevich 2006} only learns weights using STDP while delays are drawn randomly and their values frozen. Moreover, the model is evaluated on a realistic task, while models such as the tempotron are tested on simplified problems~\citep{gutig_tempotron_2006}. Foremost, the main contribution is to bring forward a model which is adapted to any spatio-temporal spiking motifs and able to be trained in a supervised manner by giving a dataset of supervision pairs. This allows a more flexible definition of the model using this properly labelled dataset instead of relying on a minute description of the physical rules governing a task, for instance the luminance conservation principle for motion detection~\citep{benosman_asynchronous_2012, dardelet}.
